Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method

### 2020-11-03 odrr5d/paper.tex
2020年11月 2日 星期一 19时07分54秒 CST

\section{Examples}
We first apply the proposed optimal rank-reduction method to a 5D synthetic data with linear/planar events, as shown in Figure \ref{fig:syn}. Figure \ref{fig:syn}(a) shows the clean synthetic data in a common offset gather. The 3D common offset gather ($t-x-y$) has been arranged into a 2D matrix. Figure \ref{fig:syn}(b) shows the noisy data with extremely strong band-limited random noise. The useful signals are almost buried in the strong noise. Figure \ref{fig:syn}(c) shows the incomplete data, where 75\% traces have been randomly decimated. The reconstructed and denoised data using three different methods, i.e., the traditional rank-reduction method (RR), the damped rank-reduction method (DRR), and the \old{optimal}\new{optimally damped} rank-reduction method (ORR), are shown in Figure \ref{fig:syn_dn}. All three methods successfully recovered most of the signals.  It is clear that the RR method causes significant residual noise, the result from the DRR method is much cleaner than that from the RR method but still contains some residual noise. The proposed ORR method, however, obtains the cleanest result among the three results shown in Figure \ref{fig:syn_dn}. To evaluate the quality of the three reconstructed data, given the exact solution in Figure \ref{fig:syn}(a), we calculate the local similarity map between each reconstructed data and the exact solution. The local similarity is a way to evaluate the similarity between two vectors/matrices/cubes in a local manner so that the evaluation can be revealed immediately from the calculated local similarity maps. The detailed introduction of mathematics behind the local similarity calculation can be found in \cite{yangkang2015ortho}. From the local similarity comparison, it is quite obvious that from the top panel (RR method) to the bottom panel (ORR method), the similarity becomes higher and higher, which indicates that the proposed method obtains the most accurate solution.

To examine the amplitude recovery quality, we select the 22nd traces from the clean data in Figure \ref{fig:syn}(a) and from the three reconstructed data in Figure \ref{fig:syn_dn}, and draw them in Figure \ref{fig:syn_amp}. Figure \ref{fig:syn_amp}(a) shows the trace-by-trace comparison in the range of the whole trace and Figure \ref{fig:syn_amp}(b) shows the zoomed trade-by-trace comparison. The zooming part is highlighted by the red transparent rectangle shown in Figure \ref{fig:syn_amp}(a). From Figure \ref{fig:syn_amp} we can see that both RR and DRR methods (blue and red lines) cause strong fluctuations in the front part of the trace, while the proposed method obtains a result (the green line) that is the closest to the exact solution (the black line). The observation is even clearer in the zoomed comparison shown in Figure \ref{fig:syn_amp}(b). Figure \ref{fig:syn_e} shows the comparison of reconstruction error. The reconstruction error is calculated as the difference between the exact solution (Figure \ref{fig:syn}(a)) and each reconstructed data shown in Figure \ref{fig:syn_dn}. From Figure \ref{fig:syn_e} we can observe that both RR and DRR cause significant error and the proposed ORR method causes negligible reconstruction error except for some observable signal energy. The reconstruction error of RR method is higher than the DRR method, mostly because of the stronger residual noise caused by the RR method. Since the reconstruction error for the proposed method is mostly negligible, the error caused by the leakage signal energy becomes more apparent. To compare the leakage signal energy among three methods, we calculate the extra noise section of the RR and DRR methods. The extra noise section refers to the extra noise compared with the reference noise section from the ORR method (Figure \ref{fig:syn_e}(c)), thus is calculated as the difference between the error from either RR or DRR method and the error from the ORR method. The extra noise sections corresponding to the RR and DRR methods are shown in Figure \ref{fig:syn_ee}. It is obvious that by calculating the extra error sections, the leakage useful energy from RR/DRR method and ORR method counteract each other and the resulting sections are mostly random noise. This observation indicates that the energy of the leakage signal for the three methods are nearly the same. We conclude from this test that despite the same damage to useful signals, the proposed method causes the least residual noise and thus obtains the cleanest reconstruction result.

@@

\AtEndDocument{
\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Clean data. (b) Noisy data. \new{Note that because of the strong random noise, the useful signals are almost buried in the noise.} (c) Incomplete data with 70\% randomly removed traces. \new{The blanks in (c) indicate where there are missing traces.} \new{The strong noise and missing traces make the data quality extremely low.} }
	\label{fig:syn}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_dn}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=10$.}
	\label{fig:syn_dn}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_simi}
	\caption{Local similarity comparison for the synthetic example (reshaped into a 2-D matrix). (a) Local similarity using the RR method. (b) Local similarity using the DRR method. (c) Local similarity using the ORR method. \new{It is obvious that the local similarity of the ORR method is much larger than the other two methods, indicating a more accurate reconstruction performance.}  }
	\label{fig:syn_dn_simi}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_amp}
	\caption{\old{Trace-by-trace comparison. (a) The whole trace. (b) Zoomed trace.}\new{Trace-by-trace comparison.  (a) Comparison in the whole trace. The black line denotes the exact solution. Green line denotes the result from the proposed method. Red line denotes the result from the DRR method. Blue line denotes the result from the RR method. (b) Zoomed trace from (a). The transparant red window highlight the zooming area.}  }
	\label{fig:syn_amp}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_e}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstruction error using the RR method. (b) Reconstruction error using the DRR method. (c) Reconstruction error using the ORR method. In this case, $rank=10$. }
	\label{fig:syn_e}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_ee}
	\caption{Extra error comparison compared with the ORR method for the synthetic example (reshaped into a 2-D matrix) when $rank=10$. (a) Extra error caused by RR method (the difference between \ref{fig:syn_e}(a) and \ref{fig:syn_e}(c)). (b) Extra error caused by RR method (the difference between \ref{fig:syn_e}(b) and \ref{fig:syn_e}(c)). }
	\label{fig:syn_ee}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H}
    \label{fig:H}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0}
    \label{fig:H0}}\\
	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H_z}
    \label{fig:H_z}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0_z}
    \label{fig:H0_z}}
	\caption{Hankel matrices for the clean and observed data for frequency slice of 30Hz. (a) Hankel matrix of the clean data. (b) Hankel matrix of the observed data. (c) \& (d) Zoomed Hankel matrices of (a) \& (b). The zooming area is highlighted by the red rectangles.}
	\label{fig:HH}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1}
    \label{fig:H1_1}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1}
    \label{fig:H2_1}}\\
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2}
    \label{fig:H1_2}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2}
    \label{fig:H2_2}}\\
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3}
    \label{fig:H1_3}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3}
    \label{fig:H2_3}}
	\caption{Hankel matrices for different methods for frequency slice of 30Hz. Left column: Hankel matrix after 1 iteration. Right: Hankel matrix after 10 iterations. Top row: Hankel matrices for the RR method. Middle row: Hankel matrix for the DRR method. Bottom row: Hankel matrix for the ORR method.}
	\label{fig:Hs}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1_z}
    \label{fig:H1_1_z}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1_z}
    \label{fig:H2_1_z}}\\
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2_z}
    \label{fig:H1_2_z}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2_z}
    \label{fig:H2_2_z}}\\
	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3_z}
    \label{fig:H1_3_z}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3_z}
    \label{fig:H2_3_z}}
	\caption{Zoomed Hankel matrices for different methods for frequency slice of 30Hz. Left column: Hankel matrix after 1 iteration. Right: Hankel matrix after 10 iterations. Top row: Hankel matrices for the RR method. Middle row: Hankel matrix for the DRR method. Bottom row: Hankel matrix for the ORR method.}
	\label{fig:Hsz}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_N5}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=5$.}
	\label{fig:syn_dn_N5}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{Fig/syn_e_N5}
	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstruction error using the RR method. (b) Reconstruction error using the DRR method. (c) Reconstruction error using the ORR method. In this case, $rank=5$. }
	\label{fig:syn_e_N5}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/synth_vars}
	\caption{SNR diagrams of the different approaches with respect to the noise level (variance value). Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}
	\label{fig:synth_vars}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/synth_ratios}
	\caption{SNR diagrams of the different approaches with respect to the sampling ratio (in percent). \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases. The ORR method always outperforms the other methods for all sampling ratios. }}
	\label{fig:synth_ratios}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/synth_ranks}
	\caption{SNR diagrams of the different approaches with respect to the selected rank. \new{The ORR method is obviously much less sensitive to the rank compared with other two methods. This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}
	\label{fig:synth_ranks}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d_3v}
    \label{fig:hyper_d_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_dn_3v}
    \label{fig:hyper_dn_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d0_3v}
    \label{fig:hyper_d0_3v}} \\   
	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) Incomplete data. \new{The blanks in (c) indicate where there are missing traces.} }
	\label{fig:hyper_N12}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N12_3v}
    \label{fig:hyper_d1_N12_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N12_3v}
    \label{fig:hyper_d2_N12_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N12_3v}
    \label{fig:hyper_d3_N12_3v}} \\ 
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N24_3v}
    \label{fig:hyper_d1_N24_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N24_3v}
    \label{fig:hyper_d2_N24_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N24_3v}
    \label{fig:hyper_d3_N24_3v}} \\    
	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The SNR comparisons are shown in Table \ref{tbl:hyper}.}
	\label{fig:hyper_dn_N12}
\end{figure}

\begin{figure}
	\centering
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N12_3v}
    \label{fig:hyper_d1_simi_N12_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N12_3v}
    \label{fig:hyper_d2_simi_N12_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N12_3v}
    \label{fig:hyper_d3_simi_N12_3v}} \\ 
	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N24_3v}
    \label{fig:hyper_d1_simi_N24_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N24_3v}
    \label{fig:hyper_d2_simi_N24_3v}}
    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N24_3v}
    \label{fig:hyper_d3_simi_N24_3v}} \\    
	\caption{Local similarity comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The introduction of local similarity is given in \cite{yangkang2015ortho}. }
	\label{fig:hyper_simi_N12}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_d0_0}
	\caption{Real data example \new{with a lot of missing traces}. \new{Because of the difficulty in display a 5D dataset, only one common midpoint gather is extracted and rearranged into a 2D matrix, and is plotted here. The two transparent colored windows denote two zooming areas for an amplified comparison.}}
	\label{fig:field_d0_0}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{Fig/field_dn_N12_0}
	\caption{Real data example. (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=20$. \new{It is obvious that all three methods obtain dramatic improvement from the raw data. The ORR method obtains cleaner and spatially more coherent seismic events compared with other two methods.}}
	\label{fig:field_dn_N12_0}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z1}
	\caption{Zoomed comparison for the field data example (the blue frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
	\label{fig:field_dn_N12_z1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z2}
	\caption{Zoomed comparison for the field data example (the red frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
	\label{fig:field_dn_N12_z2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t80}
	\caption{Comparison for constant time slice for the field data example ($t=0.32$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
	\label{fig:field_dn_N12_t80}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t160}
	\caption{Comparison for constant time slice for the field data example ($t=0.64$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
	\label{fig:field_dn_N12_t160}
\end{figure}

>>>>

\section{Examples}
We first apply the proposed optimal rank-reduction method to a 5D synthetic data with linear/planar events, as shown in Figure \ref{fig:figure1}. Figure \ref{fig:figure1}(a) shows the clean synthetic data in a common offset gather. The 3D common offset gather ($t-x-y$) has been arranged into a 2D matrix. Figure \ref{fig:figure1}(b) shows the noisy data with extremely strong band-limited random noise. The useful signals are almost buried in the strong noise. Figure \ref{fig:figure1}(c) shows the incomplete data, where 75\% traces have been randomly decimated. The reconstructed and denoised data using three different methods, i.e., the traditional rank-reduction method (RR), the damped rank-reduction method (DRR), and the \old{optimal}\new{optimally damped} rank-reduction method (ORR), are shown in Figure \ref{fig:figure2}. All three methods successfully recovered most of the signals.  It is clear that the RR method causes significant residual noise, the result from the DRR method is much cleaner than that from the RR method but still contains some residual noise. The proposed ORR method, however, obtains the cleanest result among the three results shown in Figure \ref{fig:figure2}. To evaluate the quality of the three reconstructed data, given the exact solution in Figure \ref{fig:figure1}(a), we calculate the local similarity map between each reconstructed data and the exact solution. The local similarity is a way to evaluate the similarity between two vectors/matrices/cubes in a local manner so that the evaluation can be revealed immediately from the calculated local similarity maps. The detailed introduction of mathematics behind the local similarity calculation can be found in \cite{yangkang2015ortho}. From the local similarity comparison, it is quite obvious that from the top panel (RR method) to the bottom panel (ORR method), the similarity becomes higher and higher, which indicates that the proposed method obtains the most accurate solution.

To examine the amplitude recovery quality, we select the 22nd traces from the clean data in Figure \ref{fig:figure1}(a) and from the three reconstructed data in Figure \ref{fig:figure2}, and draw them in Figure \ref{fig:figure4}. Figure \ref{fig:figure4}(a) shows the trace-by-trace comparison in the range of the whole trace and Figure \ref{fig:figure4}(b) shows the zoomed trade-by-trace comparison. The zooming part is highlighted by the red transparent rectangle shown in Figure \ref{fig:figure4}(a). From Figure \ref{fig:figure4} we can see that both RR and DRR methods (blue and red lines) cause strong fluctuations in the front part of the trace, while the proposed method obtains a result (the green line) that is the closest to the exact solution (the black line). The observation is even clearer in the zoomed comparison shown in Figure \ref{fig:figure4}(b). Figure \ref{fig:figure5} shows the comparison of reconstruction error. The reconstruction error is calculated as the difference between the exact solution (Figure \ref{fig:figure1}(a)) and each reconstructed data shown in Figure \ref{fig:figure2}. From Figure \ref{fig:figure5} we can observe that both RR and DRR cause significant error and the proposed ORR method causes negligible reconstruction error except for some observable signal energy. The reconstruction error of RR method is higher than the DRR method, mostly because of the stronger residual noise caused by the RR method. Since the reconstruction error for the proposed method is mostly negligible, the error caused by the leakage signal energy becomes more apparent. To compare the leakage signal energy among three methods, we calculate the extra noise section of the RR and DRR methods. The extra noise section refers to the extra noise compared with the reference noise section from the ORR method (Figure \ref{fig:figure5}(c)), thus is calculated as the difference between the error from either RR or DRR method and the error from the ORR method. The extra noise sections corresponding to the RR and DRR methods are shown in Figure \ref{fig:figure6}. It is obvious that by calculating the extra error sections, the leakage useful energy from RR/DRR method and ORR method counteract each other and the resulting sections are mostly random noise. This observation indicates that the energy of the leakage signal for the three methods are nearly the same. We conclude from this test that despite the same damage to useful signals, the proposed method causes the least residual noise and thus obtains the cleanest reconstruction result.

@@

\AtEndDocument{

\inputdir{synth}
\plot{figure1}{width=0.8\textwidth}{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Clean data. (b) Noisy data. \new{Note that because of the strong random noise, the useful signals are almost buried in the noise.} (c) Incomplete data with 70\% randomly removed traces. \new{The blanks in (c) indicate where there are missing traces.} \new{The strong noise and missing traces make the data quality extremely low.} }
\plot{figure2}{width=0.8\textwidth}{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=10$.}
\plot{figure3}{width=0.8\textwidth}{Local similarity comparison for the synthetic example (reshaped into a 2-D matrix). (a) Local similarity using the RR method. (b) Local similarity using the DRR method. (c) Local similarity using the ORR method. \new{It is obvious that the local similarity of the ORR method is much larger than the other two methods, indicating a more accurate reconstruction performance.} }
\plot{figure4}{width=0.8\textwidth}{\old{Trace-by-trace comparison. (a) The whole trace. (b) Zoomed trace.}\new{Trace-by-trace comparison.  (a) Comparison in the whole trace. The black line denotes the exact solution. Green line denotes the result from the proposed method. Red line denotes the result from the DRR method. Blue line denotes the result from the RR method. (b) Zoomed trace from (a). The transparant red window highlight the zooming area.} }
\plot{figure5}{width=0.8\textwidth}{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstruction error using the RR method. (b) Reconstruction error using the DRR method. (c) Reconstruction error using the ORR method. In this case, $rank=10$.}
\plot{figure6}{width=0.8\textwidth}{Extra error comparison compared with the ORR method for the synthetic example (reshaped into a 2-D matrix) when $rank=10$. (a) Extra error caused by RR method (the difference between \ref{fig:figure5}(a) and \ref{fig:figure5}(c)). (b) Extra error caused by RR method (the difference between \ref{fig:figure5}(b) and \ref{fig:figure5}(c)). }

%
%\begin{figure}
%	\centering
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H}
%    \label{fig:H}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0}
%    \label{fig:H0}}\\
%	\subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H_z}
%    \label{fig:H_z}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{Fig/H0_z}
%    \label{fig:H0_z}}
%	\caption{Hankel matrices for the clean and observed data for frequency slice of 30Hz. (a) Hankel matrix of the clean data. (b) Hankel matrix of the observed data. (c) \& (d) Zoomed Hankel matrices of (a) \& (b). The zooming area is highlighted by the red rectangles.}
%	\label{fig:HH}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1}
%    \label{fig:H1_1}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1}
%    \label{fig:H2_1}}\\
%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2}
%    \label{fig:H1_2}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2}
%    \label{fig:H2_2}}\\
%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3}
%    \label{fig:H1_3}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3}
%    \label{fig:H2_3}}
%	\caption{Hankel matrices for different methods for frequency slice of 30Hz. Left column: Hankel matrix after 1 iteration. Right: Hankel matrix after 10 iterations. Top row: Hankel matrices for the RR method. Middle row: Hankel matrix for the DRR method. Bottom row: Hankel matrix for the ORR method.}
%	\label{fig:Hs}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_1_z}
%    \label{fig:H1_1_z}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_1_z}
%    \label{fig:H2_1_z}}\\
%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_2_z}
%    \label{fig:H1_2_z}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_2_z}
%    \label{fig:H2_2_z}}\\
%	\subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H1_3_z}
%    \label{fig:H1_3_z}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{Fig/H2_3_z}
%    \label{fig:H2_3_z}}
%	\caption{Zoomed Hankel matrices for different methods for frequency slice of 30Hz. Left column: Hankel matrix after 1 iteration. Right: Hankel matrix after 10 iterations. Top row: Hankel matrices for the RR method. Middle row: Hankel matrix for the DRR method. Bottom row: Hankel matrix for the ORR method.}
%	\label{fig:Hsz}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=0.8\textwidth]{Fig/syn_dn_N5}
%	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=5$.}
%	\label{fig:syn_dn_N5}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=0.8\textwidth]{Fig/syn_e_N5}
%	\caption{Common offset gather comparison for the synthetic example (reshaped into a 2-D matrix). (a) Reconstruction error using the RR method. (b) Reconstruction error using the DRR method. (c) Reconstruction error using the ORR method. In this case, $rank=5$. }
%	\label{fig:syn_e_N5}
%\end{figure}

%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{Fig/synth_vars}
%	\caption{SNR diagrams of the different approaches with respect to the noise level (variance value). Note that the proposed approach outperforms the traditional methods more and more as the noise level increases.}
%	\label{fig:synth_vars}
%\end{figure}
%
%
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{Fig/synth_ratios}
%	\caption{SNR diagrams of the different approaches with respect to the sampling ratio (in percent). \new{It is obvious that the difference between the ORR method and the DRR method becomes larger as the sampling ratio increases. The ORR method always outperforms the other methods for all sampling ratios. }}
%	\label{fig:synth_ratios}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{Fig/synth_ranks}
%	\caption{SNR diagrams of the different approaches with respect to the selected rank. \new{The ORR method is obviously much less sensitive to the rank compared with other two methods. This phenomenon indicates that the ORR method can be applied as an adaptive method by setting a relatively large rank.}}
%	\label{fig:synth_ranks}
%\end{figure}

%\begin{figure}
%	\centering
%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d_3v}
%    \label{fig:hyper_d_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_dn_3v}
%    \label{fig:hyper_dn_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d0_3v}
%    \label{fig:hyper_d0_3v}} \\   
%	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) Incomplete data. \new{The blanks in (c) indicate where there are missing traces.} }
%	\label{fig:hyper_N12}
%\end{figure}
%
%
%\begin{figure}
%	\centering
%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N12_3v}
%    \label{fig:hyper_d1_N12_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N12_3v}
%    \label{fig:hyper_d2_N12_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N12_3v}
%    \label{fig:hyper_d3_N12_3v}} \\ 
%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_N24_3v}
%    \label{fig:hyper_d1_N24_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_N24_3v}
%    \label{fig:hyper_d2_N24_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_N24_3v}
%    \label{fig:hyper_d3_N24_3v}} \\    
%	\caption{Common midpoint gather comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The SNR comparisons are shown in Table \ref{tbl:hyper}.}
%	\label{fig:hyper_dn_N12}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N12_3v}
%    \label{fig:hyper_d1_simi_N12_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N12_3v}
%    \label{fig:hyper_d2_simi_N12_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N12_3v}
%    \label{fig:hyper_d3_simi_N12_3v}} \\ 
%	\subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d1_simi_N24_3v}
%    \label{fig:hyper_d1_simi_N24_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d2_simi_N24_3v}
%    \label{fig:hyper_d2_simi_N24_3v}}
%    \subfloat[]{\includegraphics[width=0.33\textwidth]{Fig/hyper_d3_simi_N24_3v}
%    \label{fig:hyper_d3_simi_N24_3v}} \\    
%	\caption{Local similarity comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The introduction of local similarity is given in \cite{yangkang2015ortho}. }
%	\label{fig:hyper_simi_N12}
%\end{figure}

%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{Fig/field_d0_0}
%	\caption{Real data example \new{with a lot of missing traces}. \new{Because of the difficulty in display a 5D dataset, only one common midpoint gather is extracted and rearranged into a 2D matrix, and is plotted here. The two transparent colored windows denote two zooming areas for an amplified comparison.}}
%	\label{fig:field_d0_0}
%\end{figure}
%
%
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\textwidth]{Fig/field_dn_N12_0}
%	\caption{Real data example. (a) Reconstructed data using the RR method. (b) Reconstructed data using the DRR method. (c) Reconstructed data using the ORR method.  In this case, $rank=20$. \new{It is obvious that all three methods obtain dramatic improvement from the raw data. The ORR method obtains cleaner and spatially more coherent seismic events compared with other two methods.}}
%	\label{fig:field_dn_N12_0}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z1}
%	\caption{Zoomed comparison for the field data example (the blue frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
%	\label{fig:field_dn_N12_z1}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_z2}
%	\caption{Zoomed comparison for the field data example (the red frame box). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
%	\label{fig:field_dn_N12_z2}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t80}
%	\caption{Comparison for constant time slice for the field data example ($t=0.32$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
%	\label{fig:field_dn_N12_t80}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{Fig/field_dn_N12_t160}
%	\caption{Comparison for constant time slice for the field data example ($t=0.64$s). (a) Incomplete data. (b) Reconstructed data using the RR method. (c) Reconstructed data using the DRR method. (d) Reconstructed data using the ORR method. }
%	\label{fig:field_dn_N12_t160}
%\end{figure}
